Hunting the Parent of the Orphan Stream: Identifying Stream Members \\ from Low-Resolution Spectroscopy

### 2012-10-16 2012-oss-mrs/ms.tex
Issues #5-8 resolved

Given our colour selection we expect to recover giants and contaminating dwarf contaminants. The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.

@@

Observations took place on the Anglo-Australian Telescope using the AAOmega spectrograph in April 2009. AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 392 (science and sky) targets across a $2\,^\circ$ field of view. We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm. This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$ in the blue.

The data were reduced using the standard \textsc{2DFDR} reduction pipeline\footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}. After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre. The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames. Three thirty minute science exposures were median combined to assist with cosmic ray removal. The median S/N obtained in the red arm for our fields is modest at 35 per pixel. With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg_et-al_2010}. Our spectral region also includes gravity-sensitive magnesium lines: Mg\,\textsc{I} at 8807\,{\AA}, and the Mg\,\textsc{I}\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}. As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs from giants even with weak signal.

@@

We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines. Each criterion is discussed here separately.

>>>>

Given our colour selection we expect to recover giants and contaminating dwarf contaminants. Although the 2MASS $JHK$ colours can help to separate dwarfs and giants, our target K-giants stars are too faint to be detected in the 2MASS catalogue.

@@

Observations took place on the Anglo-Australian Telescope using the AAOmega spectrograph in April 2009. AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 392 (science and sky) targets across a $2\,^\circ$ field of view. We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm. This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower spectral resolution of $\mathcal{R} \approx 1300$ in the blue.

The data were reduced using the standard \textsc{2DFDR} reduction pipeline\footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}. After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre. The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames. Three thirty minute science exposures were median-combined to assist with cosmic ray removal. The median S/N obtained in the red arm for our fields is modest at 35 per pixel. With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg_et-al_2010}. Our spectral region also includes gravity-sensitive magnesium lines: Mg\,\textsc{I} at 8807\,{\AA}, and the Mg\,\textsc{I}\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}. As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs from giants even with weak signal.

@@

We have employed a combination of separate criteria to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines. Each criteria is discussed here separately.
